Handbook streamFind: Backend

### 2023-03-08 README.Rmd

The streamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is the development and assembly of workflows for processing data from mass spectrometry and spectroscopy and for application the workflows in environmental and quality studies of the water cycle. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

@@

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) is the back-end framework for the streamFind project and can be obtained with this repository.

@@

For installation of the streamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the streamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with streamFind. The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the patRoon R package offers detailed installation instructions, including the list of required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

The streamFind R package can then be installed from the GitHub repository.

@@

The [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository.

>>>>

The streamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The goal of the streamFind project is the development and assembly of data processing workflows for mass spectrometry and spectroscopy and the application of the workflows in environmental and quality studies of the water cycle. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated functions (or modules) and the graphical user interface (GUI).

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) back-end framework is an R package.

@@

For installation of the streamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the streamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the streamFind R package. The [handbook](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites) of the patRoon R package offers detailed installation instructions, including the list of mutually required [dependencies](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#other-dependencies).

Then, the streamFind R package can then be installed from the GitHub repository.

@@

The supplementary [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository.
